### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
Acknowledgements
Adding names to section - still needs work

The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments. The Delaware County team was under the direction of Kerby Kerber.

>>>>

Thank you to Chief Scott Goldstein and former Chief Steven Lohr of the Montgomery County (MD) Department of Fire and Rescue Service for their support of this study.  Alan Butsch,   Brian Rojas,  Michael Johns, Chris Riley

The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments. The Delaware County team was under the direction of Kerby Kerber.  For construction and test support the team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection), John Hale and Todd John.

  We also thank the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.
